### 2012-03-07 doc/theses/mikula/combination_with_existing_methods_of_inference.tex
Master thesis: In progress.

\chapter{Combination with Existing Methods of Inference}
In this chapter, we describe how to incorporate the inferred statements with existing methods of XML schema inference. We focus on a class of methods which are based on a creation and subsequent simlification of the initial grammar (as discussed in Chapter \ref{chapter_analysis_of_recent_approaches}).

@@

A path represented by $PathType$ can contain variable references and association of these references with other paths. That is the reason why the normalization is convenient. It simply finds the variable references in the path and replaces them with steps from the associated paths, which are normalized recursively.

@@

>>>>

\chapter{Combination with Existing Methods of Inference}
\todo[inline]{Kontrola pomocou dat.}

In this chapter, we describe how to incorporate the inferred statements with existing methods of XML schema inference. We focus on a class of methods which are based on a creation and subsequent simlification of the initial grammar (as discussed in Chapter \ref{chapter_analysis_of_recent_approaches}).

@@

\section{Evaluation of Paths}
A path represented by $PathType$ can contain variable references and association of these references with other paths. That is the reason why the normalization is convenient. It simply finds the variable references in the path and replaces them with steps from the associated paths, which are normalized recursively.

@@

\section{Saving the Inferred Statements}
In the case of keys, the algorithm iterates through the inferred key statements. A key's context path $C$ is evaluated and the key is assigned to the target elements selected by the context path, one element can be assigned with multiple keys. Additionally, each key is assigned with a list of foreign keys that are referencing it.

In the case of inferred types, the situation is not that simple, because there can occur conflicting statements. In particular, two kinds of conflicts can emerge between two statements.

\begin{enumerate}
\item The two types do not equal, but one is castable to the other.
\item The two types do not equal and none od them is castable to the other.
\end{enumerate}

The example of conflict 1 for path $p$ without predicates is $p_1 \rightarrow date$, $p_2 \rightarrow string$. And another one is $p_1 \rightarrow byte$, $p_2 \rightarrow int$, where $p_1$, $p_2$ are paths that when stripped of predicates, they equal $p$. There are two reasons of this kind of conflicts.

The first reason is that both types are inferred correctly for nodes targeted by $p$, but one of them was inferred from a more convenient expression and is more precise. Consider these two expressions; $PathType$ $p$ is compared to an integer literal constant, and, $PathType$ $p$ is an argument of function where a formal type of the argument is byte. The first expression is utilized to infer statement $p \rightarrow integer$, and the second one to infer statement $p \rightarrow byte$. Both of the types are correct, but the second one is more accurate.
